Dual Terminal Sliding Mode Control Design For Rigid Robotic Manipulator

### 2017-07-13 paper3_manuscript.tex

\begin{abstract}
This paper proposes a dual terminal sliding mode control scheme for tracking tasks of rigid robotic manipulators. \textcolor{red}{As a signiﬁcant novelty, the presented design technique integrates the individual sliding mode  surfaces to achieve the finite time convergence of tracking errors utilizing specially designed construct, and accordingly the convergence time is easily obtained due to the integral design. The underactuated issue and input limitation are specially considered in this paper, i.e., the underactuated issue is solved by introducing the hierarchical methodology into the basic dual sliding mode controller. The proposed method can easily combine with the adaptive technique to  eliminate the negative effect caused by the input limitation in the rigorous stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the tracking tasks of the rigid robotic manipulator. Simulation results validate the theoretical analyses about the proposed method.
\end{abstract}
\begin{keyword}
Finite time control; Robotic manipulator control; Terminal sliding mode control; Input limitation; Stability analysis
\end{keyword}
\end{frontmatter}
\section{Introduction}
\textcolor{red}{Variable structure systems (VSS) are best known due to their insensitivity to parametric uncertainties~\cite{slotine1991applied}, and have been widely used in engineering applications, such as DC and DC converters~\cite{Tan2008General}, network control schemes~\cite{Hou2016}, aircrafts~\cite{Loza2015Sensor}, tethered satellite systems~\cite{Ma201667}, robotic manipulators~\cite{Beak2016A} and so on. As one important branch of the VSS, the sliding mode control (SMC) has become a popular solution to different kinds of control and signal process issues in recent years~\cite{zhao2015nonlinear,zhang2015attitude}. Meza-S{\'a}nchez et al. applied the second-order SMC scheme to a 3-DOF helicopter prototype based on the experimental test bed~\cite{meza2015output}. Zheng et al. implemented the SMC law to eliminate the negative effect of the input quantization in the coding and decoding process~\cite{zheng2016sliding}. Guzman et al. investigated the SMC application in a power factor rectifier with the constant switching frequency~\cite{guzman2016sliding}. Said et al. designed a robust adaptive sliding mode method to ensure the asymptotically stability of a boost converter~\cite{oucheriah2013pwm}. Roughly speaking, the SMC scheme is competent for normal scientific missions, due to its insensitivity to parametric uncertainties and external disturbances, however, there still exist some obstacles, such as noncontinuous switching inputs in high frequency and low convergence speed of the tracking errors~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some high-precision engineering applications~\cite{fridman2011sliding}.}

\textcolor{red}{For alleviating the mentioned bad effects, many scientific researchers have presented remarkable achievements to promote the performance of SMC in last decade~\cite{zong2013quasi,santiesteban2013time,mu2015continuous,evangelista2013lyapunov,gonzalez2014chattering,dadras2012fractional,zhao2013output}. Among these methods, the high-order SMC and super-twisting SMC work well in reducing the chattering to generate continuous inputs~\cite{castillo2015higher,palosz2015laser,edwards2016adaptive,zhao2015finite,liu2015second}. Besides the issue on repressing the chattering, the fast convergence of the SMC scheme becomes a hot subject recently. The normal linear SMC completes the stabilization of the system dynamics in two steps. In the first step, the control inputs drive the system states onto the prescript sliding mode  surfaces, and this stage is also called the reaching phase. Then the sliding mode dynamics function to drive the system states to the origins along the ideal surfaces in the second step, which is usually known as the sliding phase. The reaching phase usually requires the states to reach the ideal sliding mode surfaces in finite time, and suitably selected Lyapunov function and control parameters may accelerate this process; the sliding phase is associated with the designed ideal sliding mode  surfaces closely, and trivial design techniques can guarantee the asymptotically stability of the reduced system~\cite{mu2016switching}. To achieve a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and compared with the SMC design mentioned above, the most significant contributions of the TSM concept are introducing the finite time convergence to the sliding phase to complete the global finite time convergence~\cite{mu2016switching}. Moreover, the terminal SMC schemes have been utilized to achieve the high precise control, i.e., in~\cite{li2015robust}, an adaptive TSM controller regulated a $2$-link robotic manipulator to track the variable signals. Feng et al. stated a novel Lagrangian dynamic expression for the rigid robot, and applied the global TSM control law to manipulate the robotic dynamics ~\cite{feng2002non}. In~\cite{kamal2016continuous}, Kamal addressed a continuous homogeneous sliding mode algorithm for a perturbed second-order plant, and the algorithm could be regarded as a combination of TSM and super-twisting sliding mode schemes.}

\textcolor{red}{Notably, the conventional TSM surface design techniques are similar, since the surfaces are all designed for the single variable based on the finite time stability theory, in other words, only the individual variable and its derivative are concerned on by most designers~\cite{mu2016switching}. This nature makes the TSM controller become an individual control subsystem, which leads to the complicity of global convergence time in some extent. In this paper, an integral sliding mode  surface design technique breaks the barriers mentioned above, and the novel surface includes two designed variables to guarantee the integral finite time convergence. Moreover, nonsingularity of the TSM control scheme, chattering suppressions, underactuated applications and input limitations are also considered in the controller design.}

@@

There exist two lemmas facilitating the derivation of the finite time convergence about the DTSM controller.
\begin{mylem}
As described in~\cite{moulay2006finite}, it's assumed that the continuous function $V$ is positive definite, satisfying following conditions:
\begin{align}
\dot V\le -dV^\beta\quad\forall t\ge t_0, V(t_0)\ge 0,
\end{align}
where $d$ is a positive scalar, and $0<\beta<1$. Then the function $V$ converges to the origin for any given $t_0$, and typically the finite convergence time $t_r$ can be given as follows:
\begin{align}
t_r \le t_0+\frac{V^{1-\beta}(t_0)}{d(1-\beta)}.
\end{align}\label{lemma:1}
\end{mylem}
\begin{mylem}
Consider a second-order system:
\begin{align}
\begin{split}
\dot x_1&=-\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_2\\
\dot x_2&=-\vert x_2\vert^\alpha sgn(x_3)-x_2^3-x_1,\label{eq:normal sliding mode  surface}
\end{split}
\end{align}
and one can select the function $V = \frac{x_1^2+x_2^2}{2}$ to obtain the finite convergence time as follows~\cite{moulay2006finite}:
%since $\vert x\vert-x^\alpha+\vert x\vert \ge 0,0<\alpha<1$
\begin{align}
%t_s\le t_0+\frac{2(x_1^2+x_2^2)^{1-\alpha}}{1-\alpha}
t_s\le t_0+\frac{(2V(t_0))^{\frac{1-\alpha}{2}}}{1-\alpha},
\end{align}
where the definitions of  $t_s$, $t_0$, $\alpha$ are similar to Lemma \ref{lemma:1}. Introducing the scalar $d$ into the Eq.~(\ref{eq:normal sliding mode  surface}) obtains:
\begin{align}
\dot x_1&=-d(\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_2)\\
\dot x_2&=-d(\vert x_2\vert^\alpha sgn(x_2)-x_2^3-x_1),\label{eq:more normal sliding mode  surface}
\end{align}
the convergence time of which is
\begin{align}
t_s\le t_0+\frac{(2V(t_0))^{\frac{1-\alpha}{2}}}{d(1-\alpha)}.
\end{align}\label{lemma:2}
\end{mylem}
\textcolor{red}{For stabilization of the second-order system shown as Eq.~(\ref{eq:second-order system}), DTSM control inputs are stated according the following theorem.}
\begin{mythm}\label{theorem:1}DTSM Controller Design. The states of the system~(\ref{eq:second-order system}) will converge to origins along the surface $\bm s=0$ in finite time, if the inputs are designed as
\begin{align}
\begin{split}
u_1 &= -b_1^{-1}(\bm x)(f_1(\bm x)+\alpha\vert x_1\vert^{\alpha-1}x_2+3x_1^2x_2-x_4+k_1sgn(s_1))\\
u_2 &= -b_2^{-1}(\bm x)(f_2(\bm x)+\alpha\vert x_3\vert^{\alpha-1}x_4+3x_3^2x_4+x_2+k_2sgn(s_2)),\label{eq:DSM input}
\end{split}
\end{align}
where $k_i = l_i+\eta_i$, $i=1,2$; $\eta_i>0$ is a positive scalar value.
\end{mythm}
\begin{proof}
\textcolor{red}{For the system~(\ref{eq:second-order system}) with the sliding mode  surface~(\ref{eq:dual sliding mode  surface}), according to the equivalent control technique and the sliding mode  surface reaching condition~\cite{Arie1993sliding}, the inputs can be designed as
\begin{align}\begin{split}
u_1 &= u_{eq1}+u_{sw1}\\
u_2 &= u_{eq2}+u_{sw2}\notag
\end{split}\end{align}
where
\begin{align}\begin{split}
u_{eq1} &= -b_1^{-1}(\bm x)(f_1(\bm x)+\alpha\vert x_1\vert^{\alpha-1}x_2+3x_1^2x_2-x_4)\\
u_{eq2} &= -b_2^{-1}(\bm x)(f_2(\bm x)+\alpha\vert x_3\vert^{\alpha-1}x_4+3x_3^2x_4+x_2)\notag
\end{split}\end{align}
are the equivalent control inputs, which ensure $\dot s_1 = 0$ and $\dot s_2=0$ with $u_i = u_{eqi}$, $i=1,2$. The switching inputs can be selected as $u_{swi}=-b_i^{-1}k_isgn(s_i)$, $i=1,2$ to guarantee the finite time reaching conditions of the sliding mode  surface.}

@@

From Fig.~\ref{Figure:2}, it's apparent that all the states converge to zero as desired. \textcolor{red}{For the nominal system~(\ref{eq:simulation second-order system}) handled by utilizing the MDTSM controller, according to Eq.~(\ref{eq:total convergence time}) and simulation data, we can calculate the maximum theoretical finite convergence time $t_f=5.2609s$ directly. The system states, in other words, can be stable in no more than $5.2609s$ theoretically. However, the system response results in Fig.~\ref{Figure:2_20161108} indicate that all the states have been stable after about $1.5s$, which is far less than $t_f$. Hence, from the view of the convergence time, the simulation results are in accordance with the theoretical analyses.} Fig.~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely associated with $\eta$, for the purpose of avoiding the large chattering, the boundary layer technique is adopted. Although the states have been driven to the origin and stay there in subsequent time, one can find that the inputs don't maintain constant but fluctuate in a certain range. The nature of the situation mentioned above means that the fluctuating inputs compensate the error caused by the disturbance.\par
At this point, some effectiveness of the proposed MDTSM control scheme has been verified, and in Section \ref{sec:robotica manipulator}, we will apply it to stabilize the behavior of a $2$-link robotic manipulator directly.
\begin{figure}[http]
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig2.eps}
\caption{Phase space trajectory}
\label{Figure:2}
\end{figure}

>>>>

\begin{abstract}

This paper proposes a dual terminal sliding mode control scheme for tracking tasks of rigid robotic manipulators. \textcolor{red}{As a significant novelty, the presented design technique integrates the individual sliding mode  surfaces to achieve the finite time convergence of tracking errors utilizing specially designed construct, and accordingly the convergence time is easily obtained due to the integral design. The underactuated issue and input limitation are specially considered in this paper, i.e., the underactuated issue is solved by introducing the hierarchical methodology into the basic dual sliding mode controller. The proposed method can easily combine with the adaptive technique to  eliminate the adverse effect caused by the input limitation in the rigorous stability analysis.} These newly proposed methods also have the characteristics of nonsingularity and chattering suppression, and the effectiveness and high efficiency are verified by stabilizing the motions of the overhead crane and the tracking tasks of the rigid robotic manipulator. Simulation results validate the theoretical analyses about the proposed method.

\end{abstract}
\begin{keyword}
Finite time control; Robotic manipulator control; Terminal sliding mode control; Input limitation; Stability analysis
\end{keyword}
\end{frontmatter}
\section{Introduction}
\textcolor{red}{Variable structure systems (VSS) are best known due to their insensitivity to parametric uncertainties~\cite{slotine1991applied}, and have been widely used in engineering applications, such as DC and DC converters~\cite{Tan2008General}, network control schemes~\cite{Hou2016}, aircrafts~\cite{Loza2015Sensor}, tethered satellite systems~\cite{Ma201667}, robotic manipulators~\cite{Beak2016A} and so on. As one important branch of the VSS, the sliding mode control (SMC) has become a popular solution to different kinds of control and signal process issues in recent years~\cite{zhao2015nonlinear,zhang2015attitude}. Meza-S{\'a}nchez et al. applied the second-order SMC scheme to a 3-DOF helicopter prototype based on the experimental test bed~\cite{meza2015output}. Zheng et al. implemented the SMC law to eliminate the negative effect of the input quantization in the coding and decoding process~\cite{zheng2016sliding}. Guzman et al. investigated the SMC application in a power factor rectifier with the constant switching frequency~\cite{guzman2016sliding}. Said et al. designed a robust adaptive sliding mode method to ensure the asymptotically stability of a boost converter~\cite{oucheriah2013pwm}. Roughly speaking, the SMC scheme is competent for normal scientific missions, due to its insensitivity to parametric uncertainties and external disturbances, however, there still exist some obstacles, such as noncontinuous switching inputs in high frequency and low convergence speed of the tracking errors~\cite{boiko2013chattering,lee2009chattering}, preventing it from being utilized in some high-precision engineering applications~\cite{fridman2011sliding}.}

\textcolor{red}{For alleviating the mentioned bad effects, many scientific researchers have presented remarkable achievements to promote the performance of SMC in last decade~\cite{zong2013quasi,santiesteban2013time,mu2015continuous,evangelista2013lyapunov,gonzalez2014chattering,dadras2012fractional,zhao2013output}. Among these methods, the high-order SMC and super-twisting SMC work well in reducing the chattering to generate continuous inputs~\cite{castillo2015higher,palosz2015laser,edwards2016adaptive,zhao2015finite,liu2015second}. Besides the issue on repressing the chattering, the fast convergence of the SMC scheme becomes a hot subject recently. The normal linear SMC completes the stabilization of the system dynamics in two steps. In the first step, the control inputs drive the system states onto the prescript sliding mode  surfaces, and this stage is also called the reaching phase. Then the sliding mode dynamics function to drive the system states to the origins along the ideal surfaces in the second step, which is usually known as the sliding phase. The reaching phase usually requires the states reach the ideal sliding mode surfaces in finite time, and suitably selected Lyapunov function and control parameters may accelerate this process; the sliding phase is related to the designed ideal sliding mode  surfaces closely, and trivial design techniques can guarantee the asymptotically stability of the reduced system~\cite{mu2016switching}. To achieve a fast convergence in the sliding phase, the terminal sliding mode (TSM) control is developed based on the finite time control theory~\cite{haimo1986finite,bhat1997finite}, and compared with the SMC design mentioned above, the most significant contributions of the TSM concept are introducing the finite time convergence to the sliding phase to complete the global finite time convergence~\cite{mu2016switching}. Moreover, the terminal SMC schemes have been utilized to achieve the high precise control, i.e., in~\cite{li2015robust}, an adaptive TSM controller regulated a $2$-link robotic manipulator to track the variable signals. Feng et al. stated a novel Lagrangian dynamic expression for the rigid robot, and applied the global TSM control law to manipulate the robotic dynamics ~\cite{feng2002non}. In~\cite{kamal2016continuous}, Kamal addressed a continuous homogeneous sliding mode algorithm for a perturbed second-order plant, and the algorithm could be regarded as a combination of TSM and super-twisting sliding mode schemes.}

\textcolor{red}{Notably, the conventional TSM surface design techniques are similar, since the surfaces are all designed for the single variable based on the finite time stability theory, in another words, only the individual variable and its derivative are concerned on by most designers~\cite{mu2016switching}. This nature makes the TSM controller become an individual control subsystem, which leads to the complication of global convergence time in some extent. In this paper, an integral sliding mode  surface design technique breaks the barriers mentioned above, and the novel surface includes two designed variables to guarantee the integral finite time convergence. Moreover, nonsingularities of the TSM control scheme, chattering suppressions, underactuated applications and input limitations are also considered in the controller design.}

@@

There exist two lemmas facilitating the derivation of the finite time convergence about the DTSM controller.
\begin{mylem}
As described in~\cite{moulay2006finite}, it's assumed that the continuous function $V$ is positive definite, satisfying following conditions:
\begin{align}
\dot V\le -dV^\beta\quad\forall t\ge t_0, V(t_0)\ge 0,
\end{align}
where $d$ is a positive scalar, and $0<\beta<1$. Then the function $V$ converges to the origin for any given $t_0$, and typically the finite convergence time $t_r$ can be given as follows:
\begin{align}
t_r \le t_0+\frac{V^{1-\beta}(t_0)}{d(1-\beta)}.
\end{align}\label{lemma:1}
\end{mylem}
\begin{mylem}
Consider a second-order system:
\begin{align}
\begin{split}
\dot x_1&=-\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_2\\
\dot x_2&=-\vert x_2\vert^\alpha sgn(x_3)-x_2^3-x_1,\label{eq:normal sliding mode  surface}
\end{split}
\end{align}
and one can select the function $V = \frac{x_1^2+x_2^2}{2}$ to obtain the finite convergence time as follows~\cite{moulay2006finite}:
%since $\vert x\vert-x^\alpha+\vert x\vert \ge 0,0<\alpha<1$
\begin{align}
%t_s\le t_0+\frac{2(x_1^2+x_2^2)^{1-\alpha}}{1-\alpha}
t_s\le t_0+\frac{(2V(t_0))^{\frac{1-\alpha}{2}}}{1-\alpha},
\end{align}
where the definitions of  $t_s$, $t_0$, $\alpha$ are similar to Lemma \ref{lemma:1}. Introducing the scalar $d$ into the Eq.~(\ref{eq:normal sliding mode  surface}) obtains:
\begin{align}
\dot x_1&=-d(\vert x_1\vert^\alpha sgn(x_1)-x_1^3+x_2)\\
\dot x_2&=-d(\vert x_2\vert^\alpha sgn(x_2)-x_2^3-x_1),\label{eq:more normal sliding mode  surface}
\end{align}
the convergence time of which is
\begin{align}
t_s\le t_0+\frac{(2V(t_0))^{\frac{1-\alpha}{2}}}{d(1-\alpha)}.
\end{align}\label{lemma:2}
\end{mylem}

\textcolor{red}{For stabilization of the second-order system shown as~Eq.~(\ref{eq:second-order system}), DTSM control inputs are stated according to the following to theorem.}

\begin{mythm}\label{theorem:1}DTSM Controller Design. The states of the system~(\ref{eq:second-order system}) will converge to origins along the surface $\bm s=0$ in finite time, if the inputs are designed as
\begin{align}
\begin{split}
u_1 &= -b_1^{-1}(\bm x)(f_1(\bm x)+\alpha\vert x_1\vert^{\alpha-1}x_2+3x_1^2x_2-x_4+k_1sgn(s_1))\\
u_2 &= -b_2^{-1}(\bm x)(f_2(\bm x)+\alpha\vert x_3\vert^{\alpha-1}x_4+3x_3^2x_4+x_2+k_2sgn(s_2)),\label{eq:DSM input}
\end{split}
\end{align}
where $k_i = l_i+\eta_i$, $i=1,2$; $\eta_i>0$ is a positive scalar value.
\end{mythm}
\begin{proof}
\textcolor{red}{For the system~(\ref{eq:second-order system}) with the sliding mode  surface~(\ref{eq:dual sliding mode  surface}), according to the equivalent control technique and the sliding mode  surface reaching condition~\cite{Arie1993sliding}, the inputs can be designed as
\begin{align}\begin{split}
u_1 &= u_{eq1}+u_{sw1}\\
u_2 &= u_{eq2}+u_{sw2}\notag
\end{split}\end{align}
where
\begin{align}\begin{split}
u_{eq1} &= -b_1^{-1}(\bm x)(f_1(\bm x)+\alpha\vert x_1\vert^{\alpha-1}x_2+3x_1^2x_2-x_4)\\
u_{eq2} &= -b_2^{-1}(\bm x)(f_2(\bm x)+\alpha\vert x_3\vert^{\alpha-1}x_4+3x_3^2x_4+x_2)\notag
\end{split}\end{align}
are the equivalent control inputs, which ensure $\dot s_1 = 0$ and $\dot s_2=0$ with $u_i = u_{eqi}$, $i=1,2$. The switching inputs can be selected as $u_{swi}=-b_i^{-1}k_isgn(s_i)$, $i=1,2$ to guarantee the finite time reaching conditions of the sliding mode  surface.}

@@

From Figure~\ref{Figure:2}, it is apparent that all the states converge to zero as desired. \textcolor{red}{For the nominal system~(\ref{eq:simulation second-order system}) handled by utilizing the MDTSM controller, accrording to Eq.~(\ref{eq:total convergence time}) and simulation datas, we can calculate the maximum theoretical finite convergence time $t_f=5.2609s$ directly. The system states, in other words, can be stable in no more than $5.2609s$ theoretically. However, the system response results in Figure~\ref{Figure:2_20161108} indicate that all the states have been stable after about $1.5s$, which is far less than $t_f$. Hence, from the view of the convergence time, the simulation results are in accordance with the theoretical analyses.} Figure~\ref{Figure:3} demonstrates the inputs, the amplitudes of which are closely related to $\eta$, for the purpose of avoiding the large chattering, the boundary layer technique is adopted. Although the states have been driven to the origin and stay there in subsequent time, one can find that the inputs don't maintain constant but fluctuate in a certain range. The nature of the situation mentioned above means that the fluctuating inputs compensate the error caused by the disturbance.\par

At this point, some effectiveness of the proposed MDTSM control scheme has been verified, and in Section \ref{sec:robotica manipulator}, we will apply it to stabilize the behavior of a $2$-link robotic manipulator directly.
\begin{figure}[http]
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig2.eps}
\caption{Phase space trajectory}
\label{Figure:2}
\end{figure}
